\section{Projects}
\begin{frame}
    \frametitle{Projects}
    \framesubtitle{Software}

    The current version of our new {\nbody} code,
    written in C/C++ and CUDA, called {\GR}.

    \begin{itemize}
        \item The current version of our code,
        \begin{itemize}
            \item Using \blue{Hermite 4th order} integration scheme.
            \item Block timesteps for helping parallelism.
            \item \blue{Suitable} in the energy conservation,
                reaching errors around $\approx 10^{-9}$ and $\approx 10^{-7}$-
            \item OO.
            \item Documentation (Doxygen).
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Projects}
    \framesubtitle{Software development}

    \begin{itemize}
        \item Main software
        \begin{itemize}
            \item Main goal in the development, \blue{legibility}.
            \begin{itemize}
                \item Easy to read, modify and understand,
            \end{itemize}
            \item \blue{Balance} between optimization and maintainability.
        \end{itemize}
        \item Utility scripts.
    \end{itemize}
\end{frame}

\section{Future work}
\begin{frame}
    \frametitle{Projects}
    \framesubtitle{Milestones}

    \begin{itemize}
        \item \soft{Programming}
        \begin{itemize}
            \item<2-> Multi-GPU environment, large clusters (MPI).
            \item<3-> Assess, Parallelize, Optimize, Deploy(APOD) design cycle.
            \item<4-> Analysis of FP precision.
        \end{itemize}
        \item \soft{Physics}
        \begin{itemize}
            \item<5-> Semi-Keplerian systems
            \begin{itemize}
                \item Globular cluster + BH.
            \end{itemize}
            \item<6-> Neighbors treatment.
            \begin{itemize}
                \item Near particles are more important than the rest of the system.
            \end{itemize}
            \item<7-> Regularisations (KS, Chain, ...)
            \begin{itemize}
                \item Remove the softening parameter \soft{$\epsilon^{2}$}.
            \end{itemize}
            \item<8-> Higher order integration schemes.
            \begin{itemize}
                \item Hermite 6th order (Faster, and more accurate).
            \end{itemize}
            \item<9-> Smoothed-particle hydrodynamics (SPH).
            \begin{itemize}
                \item Different treatment for particle systems.
            \end{itemize}
            \item<10-> etc.
        \end{itemize}
    \end{itemize}
\end{frame}
